Arc Blanc: a real time ocean simulation framework

### 2025-01-20 paper.tex
Add precision on starboard

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evaluate the height of vertices in the mask}
\label{subsubsec:heightMask}
Knowing all the vertices in the mask, their height must be given as input of the FDM.
\Framework uses a simple model that tries to reproduce parts of the idea of Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}.
By construction of the grid $Z$, $M$ has a bow oriented on the positive side of the $z$ axis, and its starboard on the positive side of the $x$ axis.
Hence, $h$ is made such that from the vertex at position $\mathbf x$, the front of the mask is above the free surface and the back below, in a way that is proportional to the speed of $M$.
Moreover, the boat forms a $V$ shape, with its center a bit below the extremity of the side.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evaluate the height of vertices in the mask}
\label{subsubsec:heightMask}
Knowing all the vertices in the mask, their height must be given as input of the FDM.
\Framework uses a simple model that tries to reproduce parts of the idea of Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}.
By construction of the grid $Z$, $M$ has its bow oriented on the positive side of the $z$ axis, and its starboard (right-hand side when facing the bow) on the positive side of the $x$ axis.
Hence, $h$ is made such that from the vertex at position $\mathbf x$, the front of the mask is above the free surface and the back below, in a way that is proportional to the speed of $M$.
Moreover, the boat forms a $V$ shape, with its center a bit below the extremity of the side.
